Response to the defense feedback

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns. Developers can run the tool to analyze the side-channels leakages and fix these patterns. However, fixing all
these leakages seems not feasible in practice.  Tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography
libraries in the past decade. However,  there are
still several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
have better performance, such as the T-table lookups in AES, CRT
optimizations in RSA, and Fast Fourier Transform (FFT) in many media processing libraries. For many non-cryptography developers, side-channels are not in consideration usually. However, recent studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.

Even a minor leakage can be severe for cryptography libraries because
the leakage can reduce the encryption algorithm's strength. However,
many attacks also exploit non-cryptography libraries and applications
like machine learning
applications~\cite{yan2020cache,hong2018security}, graphic
libraries~\cite{wang2019unveiling}, spell checking
tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
cryptography libraries that exploit one vulnerability at a time,
attacks on non-cryptography rely on multiple side-channel leakage
sites to retrieve more information. Suppose one program has two
leakage sites. It is hard to estimate the total effect of those two
leakages. However, no existing tools that can estimate the total
effect of multiple leakage sites. For real-world applications with
thousands of lines, it is hard to estimate the amount of leaked
information. Attackers can guess the values of some temporary
values. And those temporary values contain some knowledge of the
original secret buffer.

Second, many side-channel leakage detection tools rely on
techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
libraries. For many other applications like machine learning, media,
and graphic libraries built on the top architecture-dependent
libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools are not able to
handle them. Moreover, some binary analysis frameworks (e.g.,
Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
floating-point instructions. However, the functionality of those
applications heavily depends on floating-point calculations.

@@

To solve the above problem, we propose a method to estimate the effect of side-channel leakages automatically. We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation. The method also allows us to combine multiple leakages sites to retrieve the information. The attack can be seen as a process that reduces the search space of the original sensitive inputs. We use the side-channel vulnerability to divide the input space. If the patterns can uniquely distinguish the input space, then we think the information is leaked totally. However, in real cases, many of these side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs. In these cases, we call them partial leakages leaks.

The method consists of three phases. In the first phase, we fuzz the target program with various inputs and collect the memory access information. In the second phase, we map the memory access information with the source code. With the debug information, we can precisely know the address access information of the source code. In the third phase, we exam the source code. If one function has two memory access patterns, then the function is vulnerable to side-channel attacks. Based on the distribution of memory access patterns under different inputs, we quantify each function's side-channel leakage.

@@

In this chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

>>>>

While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible. Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detection have shown their effectiveness in finding such code patterns. Developers can run a tool to analyze the side-channels leakages and fix these patterns. However, fixing all
these leakages seems not feasible in practice.  Tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography
libraries in the past decade. However,  there are
still several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
have better performance, such as the T-table lookups in AES, CRT
optimizations in RSA, and Fast Fourier Transform (FFT) in many media processing libraries. For many non-cryptography developers, side-channels are not in their threat model. However, recent studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.

Even a minor leakage can be severe for cryptography libraries because
the leakage can reduce the encryption algorithm's strength. However,
some attacks also exploit non-cryptography libraries and applications
such as machine learning
applications~\cite{yan2020cache,hong2018security}, graphic
libraries~\cite{wang2019unveiling}, spell checking
tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
cryptography libraries that exploit one vulnerability at a time,
attacks on non-cryptography rely on multiple side-channel leakage
sites to retrieve more information. Suppose a program has two
leakage sites. It is hard to estimate the total effect of those two
leakages. However, no existing tools that can estimate the total
effect of multiple leakage sites. For real-world applications with
thousands of lines, it is hard to estimate the amount of leaked
information. Attackers can guess the values of some temporary
values. And those temporary values contain some knowledge of the
original secret buffer.

Second, many side-channel leakage detection tools rely on
techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
libraries. For many other applications like machine learning, media,
and graphic libraries built on the top architecture-dependent
libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools are not able to
handle them. Moreover, some binary analysis frameworks (e.g.,
Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
floating-point instructions. However, the functionality of those
applications heavily depends on floating-point calculations.

@@

To solve the above problem, we propose a method to estimate the effect of side-channel leakages automatically. We treat the side-channel attack as a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation. The method also allows us to combine multiple leakages sites to retrieve the information. The attack can be seen as a process that reduces the search space of the original sensitive inputs. We use the side-channel vulnerability to divide the input space. If the patterns can uniquely distinguish the input space, then we think the information is leaked totally. However, in real cases, many of these side-channel leakage patterns are not sufficient to distinguish each leakage site but can still discern some secret inputs. In these cases, we call them partial leakages.

The method consists of three phases. In the first phase, we fuzz the target program with various inputs and collect the memory access information. In the second phase, we map the memory access information with the source code. With the debug information, we can precisely know the address access information of the source code. In the third phase, we examine the source code. If one function has two memory access patterns, then the function is vulnerable to side-channel attacks. Based on the distribution of memory access patterns under different inputs, we quantify each function's side-channel leakage.

@@
